The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-25 paper/sections/methods.tex
weight figure now wrapfig

\begin{figure}[h]
    \centering
    \includegraphics[width=3.33in]{figures/plot_distance_weight.pdf}
    \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
    }
    \label{fig:plot_distance_weight}
    \vspace{-5pt}
  \end{figure}

@@

>>>>

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=3.33in]{figures/plot_distance_weight.pdf}
%     \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
%     }
%     \label{fig:plot_distance_weight}
%     \vspace{-5pt}
%   \end{figure}

@@

\begin{wrapfigure}[11]{l}{0.31\columnwidth}
    \begin{center}
            %\vspace{-0.7cm}
            %\hspace{-0.1cm}
            \includegraphics[width=0.3\columnwidth]{figures/plot_distance_weight.pdf}

    \end{center}
    \label{fig:plot_distance_weight}
    \caption{Distance weight as a function of primary and total ray length with cutoff distance 50.}
  \end{wrapfigure}
